CTFEF

### 2023-09-06 Papers/FEDCIS-2023-presentation/cm1.tex
some more presentation stuff
more presentation stuff
final version of fedcis presentation?

\title{CTFEF }
\subtitle{Building a compiler for metaprogramming languages}
\author[name]{
	mgr. inż. Adam Grabski\\
	dr. hab. inż Ilona Bluemke
}

\institute[uni]{ Department of Electronics and Information Technology \\
Warsaw Univeristy of Technology
}
\date{\today} %Here you can change the date
\begin{document}
{

\maketitle
}%This is the colour of the first slide. bg= background and fg=foreground

@@

\input{sections/motivation.tex}
\input{sections/CTFEF.tex}

>>>>

\title{CTFEF }
\subtitle{Building a compiler for metaprogramming languages}
\author[name]{
	Adam Grabski\\
	Ilona Bluemke
}

\institute[uni]{Institute of Computer Science \\
Department of Electronics and Information Technology \\
Warsaw Univeristy of Technology
}
\date{September 18, 2023} %Here you can change the date
\begin{document}
{

\maketitle
}%This is the colour of the first slide. bg= background and fg=foreground
\AtBeginSection{}

@@

\input{sections/motivation.tex}
\input{sections/CTFEF.tex}
\input{sections/C-=-1.tex}
\input{sections/Conclusions.tex}

### 2023-09-06 Papers/FEDCIS-2023-presentation/sections/Conclusions.tex
final version of fedcis presentation?

@@

    \begin{itemize}
        \item C-=-1 performance is unsatisfactory\begin{itemize}
            \item ~10 minutes to compile 200 lines of code
        \end{itemize}
        \item Performance of the compiler was not a subject of the research, a lot of improvements are possible\begin{itemize}
            \item Currently only debug build works
            \item Interpreter data structures are inefficient (significant amount of indirection when accessing object members)
        \end{itemize}
        \item Further work is needed
    \end{itemize}

>>>>

    \begin{itemize}
        \item CTFEF architecture is flexible \begin{itemize}
            \item Several language features from other languages implemented as library features in C-=-1
            \item Generating source code of other languages at compiletime
        \end{itemize}
        \item Parts of compiler written in target language on very early stage
        \item Large amount ow work devoted to parts of compiler related to interpreting code\begin{itemize}
            \item Interpreter
            \item Defining primitive operations
            \item Bindings to LLVM
        \end{itemize}
    \end{itemize}

@@

    \begin{itemize}
        \item C-=-1 compiler performance is unsatisfactory\begin{itemize}
            \item ~10 minutes to compile 200 lines of code
        \end{itemize}
        \item Performance of the compiler was not a subject of the research, a lot of improvements are possible\begin{itemize}
            \item Currently only debug build works
            \item Interpreter data structures are inefficient (significant amount of indirection when accessing object members)
        \end{itemize}
        \item Further work is needed
    \end{itemize}
